---
title: "Homework 1: ggplot2"
author: "Aleksandra Zahharova"
date: "2019-03-07"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
```

By using *mpg* dataset:

1. Map a continuous variable to color, size, and shape. How do these aesthetics behave differently for categorical vs. continuous variables?

- Color
```{r}
mpg
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = displ)) 

```
It is not possible to assign shape to continious data.

- Size
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, size = displ)) 
```

- Shape
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, shape = class)) + 
  scale_shape_manual(values = 1:7)

```
It is not possible to assign continious data type to shape. Instead of continious data, atribute data (class) was used. 

2. What happens if you map the same variable to multiple aesthetics?

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, shape = class, color= displ, size = displ)) + 
  scale_shape_manual(values = 1:7)
``` 


3. What does the stroke aesthetic do? What shapes does it work with? (Hint: use ?geom_point)

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy,  color= class, stroke = 5 ))
```
Stroke modifies the width of the border. 


4. What happens if you map an aesthetic to something other than a variable name, like aes(colour = displ < 5)?

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, colour = displ < 5)) 
```
In this case there is continious data plays a condition role. If it is > than 5, it is false, other-true. It transfers continious data to categorical. 